### 2022-05-20 main/chapter_2ljets.tex
tidy up doubts section

\paragraph{Versus conventional}
Disappearing excesses have encouraged doubts about RJR variables;
the existence of the `RJR-mimic' paper~\cite{atlas_rjr_mimic_SUSY_2018_06}
is public evidence of this.

A more precise problem is that that phase space selected by RJR regions tends
to be poorly (inaccurately or imprecisely) modelled by simulations.
This is plausibly explained how RJR variables are not simply related to
conventional, lab-frame variables.
Simulations have been tuned to model conventional variables well, and
`systematic' variations also are evaluated and derived in conventional variables.
Not all functions of the data are well understood.

A lack of reliable simulations motivates reliance on `data-driven' background
estimates, which, from my perspective, are hard to interpret or trust.
For these reasons, the $\twoljets$ electroweak analysis uses only conventional
event variables.

>>>>

\paragraph{Doubts}
Disappearing excesses have encouraged some doubts about RJR variables in
certain social circles;
the existence of the `RJR-mimic' paper~\cite{atlas_rjr_mimic_SUSY_2018_06}
is public evidence of this.

A more precise frame problem with RJR variables is that they select phase space
which tends to be poorly modelled by simulations.
This is plausibly explained by the fact that  RJR variables are non-trivially
related to conventional, lab-frame variables.
Simulations have been tuned to model conventional variables well, and
`systematic' variations are evaluated and derived in conventional variables.
Not all functions of the data are well understood.
These effects cause Monte Carlo simulations to give predictions in RJR regions
which are inaccurate and/or carry large uncertainties.

A lack of reliable simulations motivates reliance on `data-driven' background
estimates, which, from my perspective, are hard to interpret or trust.
For these reasons, the $\twoljets$ electroweak analysis does not use any
RJR event variables.
